Keyword and Collocation analysis on India-related text of Natural History

### 2023-06-23 paper_quarto.qmd
first draft update

As mentioned earlier, the digitized text of *Natural History* with geographical annotations is readily accessible through the [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project. In order to facilitate the analysis, I conducted a scraping of the full text, exporting it as a **reference corpus** in .txt format. Furthermore, I extracted the texts specifically associated with the Indian subcontinent, utilizing the annotated coordinates, creating a **target corpus** of geographically related texts focused on India. The scraping was conducted with [Beautiful Soup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in Python, and the [code](https://github.com/lizaodawn/zhuang/blob/papertry/Natural%20History_corpus%20scrape.ipynb) is uploaded to the same repository of the project.[^1]

@@

ref_flist <- freqlist(fnames_wholetext, re_token_splitter = re("\\s+"))
tar_flist <- freqlist(fnames_indiatext, re_token_splitter = re("\\s+"))
```

The **target corpus** consists of all text related to Indian subcontinent (with coordinates in range of *8°4'N-37°6'N and 68°7'E to 97°25'E*), segregated by paragraphs, containing `r prettyNum(n_tokens(tar_flist))` tokens and `r n_types(tar_flist)` types, with the type-token ratio of `r round(n_types(tar_flist)/n_tokens(tar_flist), 2)`.

And the **reference corpus** consists of all texts in *Natural History*, segregated by paragraphs, consisting of `r prettyNum(n_tokens(ref_flist))` tokens and `r n_types(ref_flist)` types, with the type-token ratio of `r round(n_types(ref_flist)/n_tokens(ref_flist), 2)`.

@@

The frequency lists for the **target corpus** (Indian subcontinent related texts) and **reference corpus** (whole text) are generated respectively, and the association scores are calculated through the [assoc_scores](https://masterclm.github.io/mclm/reference/assoc_scores.html) function. The association score is filtered based on the criteria of both PMI and $G^2$ scores, requiring a minimum score of 2. This criterion ensures that the selected words have a probability at least four times higher than the overall data, along with statistically significant supporting evidence [@methods], allowing to identify the most statistically significant keywords in India-related texts when compared to the reference corpus.

@@

Significantly, a substantial number of the keywords in the India-related text revolve around goods, particularly precious stones, suggesting a prominent thematic focus. The presence of keywords such as "beryls", "obsidian", "bdellium", "agates", "callaina", "prasii", "carnelian" and "sandastros" indicates the involvement of various gemstones and goods associated with India. These findings are complemented by the presence of keywords like "condensation", "merchandize" and "peppertree" which suggest the production and trade of goods between the Roman Empire and the Indian subcontinent during that era.

>>>>

As mentioned earlier, the digitized text of *Natural History* with geographical annotations is readily accessible through the [TOPOSText](https://topostext.org/work/148 "Check Natural History on ToposText") project. In order to facilitate the analysis, I conducted a scraping of the full text, exporting it as a **reference corpus** in .txt format. Furthermore, I extracted the texts specifically associated with the India, utilizing the annotated coordinates, creating a **target corpus** of geographically related texts focused on India. The scraping was conducted with [Beautiful Soup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in Python, and the [code](https://github.com/lizaodawn/zhuang/blob/papertry/Natural%20History_corpus%20.ipynb) is uploaded to the same repository of the project.[^1]

@@

# build frequency list for reference corpus
flist_ref <- fnames_wholetext %>%
  freqlist(re_token_transf_in = "[[:punct:]]", # Match punctuation marks
           token_transf_out = "")

# build frequency list for target corpus
flist_target_all <- fnames_indiatext %>%
  freqlist(re_token_transf_in = "[[:punct:]]", # Match punctuation marks
           token_transf_out = ""
    ) 
```

The **target corpus** consists of all text related to India (with coordinates in range of *8°4'N-37°6'N and 68°7'E-97°25'E*), segregated by paragraphs, containing `r prettyNum(n_tokens(flist_target_all))` tokens and `r n_types(flist_target_all)` types, with the type-token ratio of `r round(n_types(flist_target_all)/n_tokens(flist_target_all), 2)`. [^2]

[^2]: Given the challenges in precisely determining the coordinate range during the 1st century BC, the coordinate range of modern India is applied as a rough approximation.

And the **reference corpus** consists of all texts in *Natural History*, segregated by paragraphs, consisting of `r prettyNum(n_tokens(flist_ref))` tokens and `r n_types(flist_ref)` types, with the type-token ratio of `r round(n_types(flist_ref)/n_tokens(flist_ref), 2)`.

@@

The frequency lists for the **target corpus** (India-related texts) and **reference corpus** (whole text) are generated respectively, and the association scores are calculated through the [assoc_scores](https://masterclm.github.io/mclm/reference/assoc_scores.html) function. The association score is filtered based on the criteria of both PMI and $G^2$ scores, requiring a minimum score of 2. This criterion ensures that the selected words have a probability at least four times higher than the overall data, along with statistically significant supporting evidence [@methods], allowing to identify the most statistically significant keywords in India-related texts when compared to the reference corpus.

@@

Significantly, a substantial number of the keywords in the India-related text revolve around goods, particularly precious stones, suggesting a prominent thematic focus. The presence of keywords such as "beryls", "obsidian", "bdellium", "agates", "callaina", "prasii", "carnelian" and "sandastros" indicates the involvement of various gemstones and goods associated with India. These findings are complemented by the presence of keywords like "condensation", "merchandize" and "peppertree" which suggest the production and trade of goods between the Roman Empire and the Indian regions during that era.
